### 2017-03-29 thesis/latex/thesis.tex
Thesis: mini commit.

@@

\section{Chapter: Introduction}

Begin with a paper-like introduction which talks about:

>>>>

\usepackage{csquotes}

@@

\section{Chapter: Introduction}
\blockquote{An embryo in its spherical blastula stage has spherical symmetry [...]. But a system which has spherical symmetry, and whose state is changing because of chemical reactions and diffusion, will remain spherically symmetrical for ever [...]. It certainly cannot result in an organism such as a horse, which is not spherically symmetrical. \textbf{Alan Turing, The Chemical Basis of Morphogenesis, 1952}}

Cells need to create asymmetric, heterogeneous structures inside themselves in order to function. However, as per the above quote, diffusive processes cannot create this asymmetry. How then do cells create heterogeneity? Motor proteins are part of the answer. Motor proteins are structures which use energy to create directed motion in cells. In broad terms, they are creators of asymmetry. This thesis will explore a hypothesis on how one such motor protein, Dynein, generates directed motion.\\

\subsection{Interest builder}
Begin with a paper-like introduction which talks about:
